### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update
Chicago: Edit author list

\headerC{
{
\flushright{
Craig G. Weinschenk \\
Daniel Madrzykowski \\
Kristopher J. Overholt \\

@@

\headerC{
\flushright{
Craig G. Weinschenk \\
Daniel Madrzykowski \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty. Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature). For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power. Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}. More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

@@

In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident). The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur. The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to 5~MW as the oxygen inside the structure is consumed. There is an insufficient amount of oxygen in the structure to combust all of the fuel, therefore combustion occurs locally at the vents where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s. After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW. The HRR then increases towards a sustainable steady-state value.

>>>>

\headerC{
{
\flushright{
Craig G. Weinschenk \\
Kristopher J. Overholt \\
Daniel Madrzykowski \\

@@

\headerC{
\flushright{
Craig G. Weinschenk \\
Kristopher J. Overholt \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty. Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature). For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power. Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}. More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S. Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

@@

In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident). The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur. The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to 5~MW as the oxygen inside the structure is consumed. There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s. After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW. The HRR then increases towards a sustainable steady-state value.
